Work Stress

### 2023-03-15 outputs/paper/paper.qmd
Update paper to include new additions into Introduction

Work is the most common cause of many people to get stress. Work stress can be found in many forms for people. In this paper, we will examine job status, work hours, industry sector, satisfaction rate of your job into the correlation of work stress levels. There are many analysis to talk about relevant to work stress.

>>>>

Work is the most common cause of many people to get stress. Work stress can be found in many forms for people. In this paper, we will examine job status, work hours, industry sector, satisfaction rate of your job into the correlation of work stress levels. There will be context that will motivate such as the data that is representing the factors of work stress and how people feel based on the real dataset. There are many analysis to talk about relevant to work stress, that can later conclude the next steps that workplace should consider to reduce work stress for many employees. All of the data are being collected through GSS, which allowed us to create different figures of job status, work hours, industry sector, and satisfaction rates. They were all written as code within the Quarto document. We saw some data that shows how the work stress occurs from the these factors. All of these information within the paper is very important because it will let the readers and others in the public to be aware of how people are facing work stress, and the analysis can provide some strong points that can lead everyone to know what employers and managers can do to avoid work stress for all employees working.
